First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-03 ms.tex
Slight rewording for clarification
Attempt at writing RTS bandpass cal sentences.

Besides RFI, we manually flag data to remove three other effects. As mentioned in 
Section~\ref{sec:MWA}, the edges of the coarse bands contain high levels of aliasing from 
the filter applied in the digital receivers. We flag two 40 kHz channels on either side of the 
coarse band edges (total of four channels per coarse band edge). In principle the aliasing 
could be calibrated out and these channels could be recovered, but this is left for future 
work. Second, early data from the MWA also contained some instances where antennas 
were not pointed properly at the beginning of observations due to a beamformer error. This 
problem has since been resolved, but exists in our data. We therefore flag the first two 
seconds of each observation to avoid any potentially mis-pointed data. 
Finally, we flag the central fine channel of each coarse band. This channel corresponds
to the sub-band DC mode, which has been observed to contain anomalous power likely
due to very low level rounding errors in the polyphase filter bank of the digital receivers.

@@

The two dimensional power spectrum is a useful figure of merit (FoM) \textbf{(the PS is more of a tool than a FoM)} as we improve and 
refine our analysis pipeline. Foregrounds and systematics often manifest with characteristic 
shapes in this space, enabling us to diagnose problems and quantify improvements 
\citep{Morales:2012}. We use the MWA 3 hour ``golden'' data set from August 23, 2013, to 
repeatedly form power spectra to test and refine our analysis. While an exhaustive catalog 
of these improvements would be unsuited for this article (and likely bore the reader), we 
demonstrate the utility of the 2D power spectrum as a FoM with a few key techniques we 
have employed in our analysis.

@@

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. The primary differences lie in the 
bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
calibration model uses a model with 1000 sources, for which ionospheric corrections are 
estimated and applied, before peeling of those sources from the dataset. The bandpass 
calibration is fundamentally different to FHD... \textbf{**BART: please also include a mention of 
the 150m cable reflection and why we may not expect to see it with RTS**.} The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.

>>>>

Besides RFI, we manually flag data to remove three other effects. As mentioned in 
Section~\ref{sec:MWA}, the edges of the coarse bands contain high levels of aliasing from 
the filter applied in the digital receivers. We flag two 40 kHz channels on either side of the 
coarse band edges (total of four channels per coarse band edge). In principle the aliasing 
could be calibrated out and these channels could be recovered, but this is left for future 
work. Second, early data from the MWA also contained some instances where antennas 
were not pointed properly at the beginning of observations due to a beamformer error. This 
problem has since been resolved, but exists in our data. We therefore flag the first two 
seconds of each observation to avoid any potentially mis-pointed data. 
Finally, we flag the central 40 kHz channel of each coarse band. This channel corresponds
to the sub-band DC mode, which has been observed to contain anomalous power likely
due to very low level rounding errors in the polyphase filter bank of the digital receivers.

@@

The two dimensional power spectrum is a useful figure of merit (FoM) as we improve and 
refine our analysis pipeline. Foregrounds and systematics often manifest with characteristic 
shapes in this space, enabling us to diagnose problems and quantify improvements 
\citep{Morales:2012}. We use the MWA 3 hour ``golden'' data set from August 23, 2013, to 
repeatedly form power spectra to test and refine our analysis. While an exhaustive catalog 
of these improvements would be unsuited for this article (and likely bore the reader), we 
demonstrate the utility of the 2D power spectrum as a FoM with a few key techniques we 
have employed in our analysis.

@@

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. The primary differences lie in the 
bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
calibration model uses a model with 1000 sources, for which ionospheric corrections are 
estimated and applied, before peeling of those sources from the dataset. The bandpass 
calibration is fundamentally different to FHD.
The bandpass for each antenna is fit to a 2nd order polynomial within each 1.28~MHz coarse 
band individually. The delay of the 150~m cable reflection discussed earlier is comparable
to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
data \citep{Jacobs:2016}.
The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.
